---
title: "Codebook"
author: "fleschgordon"
date: "8 Juni 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r, include=FALSE}
load(file="dtActivityMean.RData")
load(file="dtActivityLabels.RData")
```

This is Codebook a describes the variables, the data, and any transformations or work, which is in the `run_analysis.R` to clean up and aggregate the data to produce the end result the `ActivityMean.txt`
:

##Data
The input data is downloaded for this url "https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip"
and contains Samsung Galaxy S smartphone activity tracking data.
the following files were used:

* ActivityLabels from  `/test/y_test.txt` and `/train/y_train.txt`
* Activities from `/test/X_test.txt` and `/train/X_train.txt`
* Subjects from `/test/subject_test.txt` and `/train/subject_train.txt`
* Features from `/features.txt`

##Transformation steps
All dataset uses `data.tables` because of flexibility and performance.

1. Merges the training and the test sets to create one data set.
```{r, eval=FALSE, include=TRUE}
dtActivity <- rbind(dtActivityTrain, dtActivityTest)
```

2. Extracts only the measurements on the mean and standard deviation for each measurement.
```{r, eval=FALSE, include=TRUE}
#only mean or std features
dtFeaturesFinal <- dtFeatures[grep("mean|std", dtFeatures$featureName), ]
dtFeaturesFinal$featureName <- gsub('-mean', 'Mean', dtFeaturesFinal$featureName)
dtFeaturesFinal$featureName <- gsub('-std', 'Std', dtFeaturesFinal$featureName)
dtFeaturesFinal$featureName <- gsub('[-()]', '', dtFeaturesFinal$featureName)
```

3. Uses descriptive activity names to name the activities in the data set
```{r, eval=FALSE, include=TRUE}
dtActivityFinal <- merge(dtActivityFinal, dtActivityLabels, by= "activityID", all.x = TRUE)
```

4. Appropriately labels the data set with descriptive variable names.
```{r, eval=FALSE, include=TRUE}
setnames(dtActivityLabels, names(dtActivityLabels), c("activityID", "activityName"))
```
```{r, echo=TRUE}
dtActivityLabels
```

5. From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.

```{r, eval=FALSE, include=TRUE}
dtActivityMean <- dcast(dtActivityTidyFinal, subjectID + activityID ~ featureName, mean)
write.table(dtActivityMean, "./data/ActivityMean.txt", row.names = FALSE, quote = FALSE)
```



##Result File ActivityMean.txt
###Keys
* subjectID : ID of the subject
* activityID : ID of the activity

###Structure
* Keys
* Measurements


```{r str(dtActivityMean), echo=TRUE}
str(dtActivityMean)
```



